Technical Report

### 2017-11-29 fully-abstract-comp/technical-report.tex
fixed a couple of typos
Added the non ret-token case in L lr. Not sure whether we will need this.
typos

% \dominique{7-9-2017: Should we keep local/global and linear/non-linear?  I was thinking just the latter would suffice...}
% \lau{07-09-2017: The local/global mechanism still has some value as it now can be used for the purpose of arguments that cannot be stored by the receiver (if you are willing to ``pay'' the clearing cost). I do, however, not think that it is strictly necessary here to make things work.}
% \lau{12-09-2017: I will remove the local capabilities today for the reasons we have discussed (they add to the complexity and they seem to be of little to no use without a clear memory instruction).}
Source language domains:
\[
  \begin{array}{rrcl}
   \addrbnf,\basebnf \in & \Addr & \defeq & \nats \\
    \sealbasebnf, \sigma \in & \Seal & \defeq & \nats \\
    &\Word & \defeq & \ints \uplus \SealableCaps\\
    \permbnf \in& \Perm & \defbnf & \dots \\
    &\linbnf & \defbnf & \linear \mid \normal \\
    &\aendbnf & \in & \Addr \uplus \{\infty \} \\
    &\sealendbnf & \in & \Seal \uplus \{\infty \} \\
    &\scbnf &\defbnf & ((\permbnf,\linbnf),\basebnf,\aendbnf,\addrbnf) \mid \seal{\linbnf,\sealbasebnf,\sealendbnf,\sigma}\\
    & & & {\sourcecolor{} \mid \stkptr{\permbnf,\basebnf,\aendbnf,\addrbnf}}\\ 
    &\cbnf & \defbnf &  \scbnf \mid \sealed{\scbnf,\sigma}{\sourcecolor{} \; \mid \retptrd(\sigma,(\basebnf,\aendbnf)) \mid \retptrc(\sigma,(\permbnf,\linbnf,\basebnf,\aendbnf,\addrbnf))}\\ 
    &\rbnf & \defbnf &\pcreg \mid \rret \mid \rstk \mid \rdata \mid \dots \\
    &\Reg & \defeq & \RegName \fun \Word\\
    &\Mem & \defeq & \Addr \fun \Word \\
    &\MemSeg & \defeq & \Addr \parfun \Word \\
    {\sourcecolor \sstkframe \in} & {\sourcecolor \StkFrame} & {\sourcecolor \defeq} & {\sourcecolor \Caps \times \MemSeg \times \Addr}\\
    \src{\sstk \in}& \src{ \Stack} & \src{ \defeq} & \src{ \StkFrame^*} \\
    \Phi \in & \ExecConf & \defeq & \Mem \times \Reg {\sourcecolor{} \; \times \; \Stack \times \MemSeg }\\
    &\Conf & \defeq & \ExecConf \uplus \{\failed\} \uplus (\{\halted\} \times \Mem)
  \end{array}
\]
\lau{06-09-2017: Should seals also have the option to be linear?}
\lau{13-09-2017: For now I have added linearity to the seals.}
\dominique{27-9-2017: I think we should have versions of $\retptrd$ and $\retptrc$ for non-top stack frames and define that invoking them with the current stack pointer will fail.}
\lau{28-09-2017: Why would you like this? If we want to add this, we will have to be careful, because an old code-return-pointer may fit perfectly well with our new data-return-pointer, so in this case it should not fail. We added the seal to the return pointers, so we had some way of figuring out whether two return pointers would actually fit together.}
\dominique{27-9-2017: Likewise, I think we need to have a source-language representation for a pointer into one of the non-top stack frames, as we may need to be able to back-translate adversary code that reads/writes in those.}
\lau{28-09-2017: At the moment, the only part of the stack that is stored in the stack frame is the private part. Specifically it is the part from the base to the current address of the stack pointer \emph{in $r_\stk$}. This means that if someone saves a stack pointer, so it is not included in the call, then they can still use it because that part of the stack was not encapsulated in a stack frame. Makes sense?}
The target language domains are all the non blue parts in the above. The source language domains are the black and blue parts in the above. Further
\begin{itemize}
\item $\linbnf$ defines domain $\Linear$
\item $\scbnf$ defines domain $\SealableCaps$
\item $\cbnf$ defines domain $\Caps$
\item $\rbnf$ defines the finite set $\RegName$.
\item $\Perm$ is defined as the set of permissions in Figure~\ref{fig:perm-hier}.
\end{itemize}

@@

\[
  \isLinear{\cb} \defeq
  \begin{cases}
    \top & 
    \arraycolsep=0pt
    \begin{array}[t]{l}
      \cb = ((\_,\linear),\_,\_,\_) \tor\\
      \cb = \seal{\linear,\_,\_,\_} \tor\\
      \cb = \sealed{\cb',\_} \tand \isLinear{\cb'} 
    \end{array}\\
    \src{\top} & 
    \sourcecolor\left.
    \arraycolsep=0pt
    \begin{array}[t]{l}
      \cb = \stkptr{\_,\_,\_,\_}\\
      \cb = \retptrd(\_,\_)
    \end{array}\right.\\
    \bot & \totherwise
  \end{cases}
\]

@@

\noindent\textbf{xjmp}\\
\lau{22-09-2017: Can we allow the callee to return any stack pointer? At the moment, it is not possible to create an empty stack pointer which may be a saving grace. If we at some point change this, so you can split capabilities into empty ones, then we need to consider whether it is safe for callees to return empty stacks (I think it is okay as long as we always have some stack usage).}
\lau{28-09-2017: For now, the jump to a return pointer does the stack end point check. We could possibly move this to the proposed semantic condition as well.}
\begin{align*}
  \sem{\txjmp{r_1}{r_2}}(\Phi) = &
                                   \begin{cases}
                                     \arraycolsep=0pt
                                     \begin{array}[t]{rl}
                                       \Phi & \updReg{r_1}{w_1}\\
                                            & \updReg{r_2}{w_2}\\
                                            & \updReg{\pcreg}{c_\code}\\
                                            & \updReg{\rdata}{c_\data}
                                     \end{array} &
                                     \begin{array}[t]{l}
                                       \Phi(r_1) = \sealed{c_\code,\sigma} \tand \\
                                       \Phi(r_2) = \sealed{c_\data,\sigma} \tand \\
                                       \nonExec{c_\data} \tand \\
                                       w_1 = \linCons{\Phi(r_1)} \tand \\
                                       w_2 = \linCons{\Phi(r_2)}
                                     \end{array}
                                     \\&\\
                                     \sourcecolor\left.
                                       \arraycolsep=0pt
                                       \begin{array}[t]{rl}
                                         \Phi' & \updReg{r_2}{0} \\
                                               & \updReg{\pcreg}{\opc}\\
                                               & \updReg{\rdata}{0}\\
                                               & \updReg{\rstk}{c_\stk}
                                       \end{array}\right.&
                                     \sourcecolor\left.
                                       \begin{array}[t]{l}
                                         \Phi(r_1) = \retptrc(\sigma,\_) \tand \\
                                         \Phi(r_2) = \retptrd(\sigma,(\aaddr_\stk,\_)) \tand \\
                                         \Phi(\rstk) = \stkptr{\rw,\stkb,\eaddr_\stk,\_} \tand \\
                                         \Phi = (\mem,\reg,\stkf::\stk,\ms_\stk) \tand \\
                                         \stkf = (\opc,\ms_{\stk,\priv}) \tand \\
                                         \dom(\ms_{\stk,\priv}) = [\eaddr_\stk+1,\eaddr_{\stk,\priv}] \tand\\
                                         c_\stk = \stkptr{\rw,\stkb,\eaddr_{\stk,\priv},\aaddr_\stk} \tand\\
                                         \Phi' = (\mem,\reg,\stk,\ms_{\stk,\priv} \uplus \ms_\stk) 
                                       \end{array}\right.
                                     \\
                                     \failed & \totherwise
                                   \end{cases}
\end{align*}

\noindent\textbf{cseal}\\
\begin{align*}
  \sem{\tcseal{r_1}{r_2}{r_3}}(\Phi) = &
                                  \begin{cases}
                                    \updPcAddr{}\left(
                                    \arraycolsep=0pt
                                    \begin{array}{rl}
                                      \Phi&\updReg{r_1}{\vsc}\\
                                          &\updReg{r_2}{w_2}
                                    \end{array}\right)
&
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \Phi(r_2) \in \SealableCaps \tand \\
                                      \Phi(r_3) = \seal{\lin, \sigma_\baddr, \sigma_\eaddr,\sigma} \tand \\
                                      \sigma_\baddr \leq \sigma \leq \sigma_\eaddr \tand \\ 
                                      \vsc = \sealed{\Phi(r_2),\sigma} \tand\\
                                      w_2 = \linCons{\Phi(r_2)}                                     
                                    \end{array}
                                    \\
                                    \failed & \totherwise
                                  \end{cases}
\end{align*}

@@

                                                   \Phi(r_1) = \sealed{c_1,\sigma_1} \tand \\
                                                   \Phi(r_2) = \sealed{c_2,\sigma_2} \tand \\

@@

\subsubsection{Programs}
Here we define what constitutes a program.
\lau{05-10-2017: It seems like both program and context takes care of linking atm.}
\begin{definition}
  \label{def:program}
  \lau{27-09-2017: The ``somehow''s need to be fixed.}
  A program, $\program$ consists of two sealed capabilities, $\vsc_\code = \sealed{c_\code,\sigma}$ and $\vsc_\data = \sealed{c_\data,\sigma}$, and and two memory segments $\ms$ and $\ms_\link$ satisfying
  \begin{itemize}
  \item $c_\code = ((\rx,\lin_\code),\baddr_\code,\eaddr_\code,\aaddr_\code)$ where $\aaddr = \baddr + 2$ and $[\baddr_\code,\eaddr_\code]\subseteq \dom(\ms)$
  \item $c_\data = ((\rw,\lin_\data),\baddr_\data,\eaddr_\data,\baddr_\data)$ where $[\baddr_\data,\eaddr_\data] \subseteq \dom(\ms)$ and $[\baddr_\code,\eaddr_\code] \cap [\baddr_\data,\eaddr_\data] = \emptyset$
  \item $\ms$ and $[c_\code,c_\data]$ are self-contained with $\ms_\link$ as slack.
  \item $\ms$ respects write-xor-execute.
  \item $\ms(\baddr_\code) = \seal{\normal,\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}$ where these are somehow the sufficient amount of seals.
  \item $\ms(\baddr_\code+1) = ((\ro,\normal),\baddr_\link, \eaddr_\link, \baddr_\link)$ where $\dom(\ms_\link) = [\baddr_\link, \eaddr_\link]$
  \end{itemize}
\end{definition}
\lau{27-09-2017: At the moment, we do not have the proper support to let the code capability be linear (in the sense that you cannot write a sensible program) - maybe we should just require the code capability to be normal.}

@@

\[
  \lrk(W) = \left\{ \npair{\left(\array{l}\src{\retptrc(\sigma,(\perm,\lin,\baddr_c,\eaddr_c,\aaddr_c))},\\\src{\retptrd(\sigma,(\aaddr_d,\eaddr_d))},\\k_{c,T},k_{d,T}\endarray\right)} \middle|
    \begin{array}{l}
      k_{d,T} = \sealed{\sigma,c_d} \wedge\\
      k_{c,T} = \sealed{\sigma,c_c} \wedge\\
      c_c = ((\perm,\lin),\baddr_c,\eaddr_c,\aaddr_c) \wedge\\
      c_d = ((\rw,\linear),\aaddr_d,\eaddr_d,\aaddr_d-1) \wedge\\
      \npair[n]{[\stpair[.]{\retptrc(\sigma,\_)}{k_{c,T}},\stpair[.]{\retptrd(\sigma,\_)}{k_{d,T}}]} \in \lrp(W) \wedge \\
      \forall n' \leq n, W' \pubft W \ldotp \\
      \quad \forall W_\lrr, W_\lrm \ldotp  \\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk::(\opc,\ms_{\stk,f}),\ms_\stk}{\ms_T}}{W_\lrm} \wedge \\
      \qquad\opc = c_c \wedge\\
      \qquad\dom(\ms_{\stk,f}) = [\aaddr_d,\eaddr_d] \wedge\\
      \qquad\npair[n']{\array{l}\src{\reg_S\update{\rstk}{\stkptr{\rw,\stkb,\eaddr_d,\aaddr_d}}},\\
                               {\reg_T\update{\rstk}{((\rw,\linear),\stkb,\eaddr_d,\aaddr_d)}}\endarray}\in \lrr(\{r_\stk\})(W_\lrr) \wedge\\ 
      \qquad\npair[n']{[(\opc,\opc)]} \in \lrp(W')\\
      \qquad\Rightarrow\\
      \qquad \npair[n']{\left(\arraycolsep=0pt\array{l}
                          \left(\arraycolsep=0pt\array{l}
                            \src{\ms_S,\reg_S\update{\pcreg,\rstk}{\opc,\stkptr{\rw,\stkb,\eaddr_d,\aaddr_d}},}\\
                            \src{\stk, \ms_\stk \uplus \ms_{\stk,f}}
                          \endarray \right) \\
                          \left(\ms_T,\reg_T\update{\pcreg,\rstk}{\opc,((\rw,\linear),\stkb,\eaddr_d,\aaddr_d)} \right)
                        \endarray \right)} \in \lro(W'\oplus W_\lrr \oplus W_\lrm)
    \end{array}
  \right\}
\]

@@

\[
  \lrr(R)(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : \RegName \fun \World \ldotp \\
      \quad W = \bigoplus_{r \in \RegName} S(r) \\
      \quad \forall r \in \RegName \setminus (\{\pcreg \} \cup R)\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrv(S(r))
    \end{array}
            \right\}
\]
Where $S\text{ is a separation of $W$}$ means that no two partition share the same ``spatial'' region (whatever that is).
\lau{TODO: Rewrite the other definitions to pass around $H_\sigma$ (if this is how we want to handle seals.)}
\[
  \lrv(H_\sigma,W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrc(\sigma,\perm,\lin,\baddr,\eaddr,\aaddr)},\\\sealed{\sigma,\vsc_C}\endarray\right)} \;\middle| \;
    \begin{array}{l}
      \vsc_c = ((\perm,\lin),\baddr,\eaddr,\aaddr) \wedge \\
      \forall (\src{c},c') \in H_\sigma(\sigma) \ldotp \\
      \quad \exists r \in \addressable(\linear,W) \ldotp \\
      \qquad  \exists \stpair{\ms}{\ms} \ldotp \\
      \qquad \quad \dom(\src{\ms_S}) = \dom(\ms_T) = [\pi_\baddr(c), \pi_\eaddr (c)] \wedge \stareg{\spao} \nequal W(r) \wedge \\
      \qquad \qquad \forall W' \privft W \ldotp \\
      \qquad \qquad \quad \exists r', W'(r') = W(r), \exists r'', W'(r'') = \stdreg{[\stkb,\eaddr]}{\spao} \ldotp \\
      \qquad \qquad \qquad { \color{red} \npair{(\src{\retptrc(\sigma,\perm,\lin,\baddr,\eaddr,\aaddr)}, \src{c}, \sealed{\sigma,\vsc_c}, c')}} \in \lrk(W')
    \end{array}
    \right\}\cup\\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrd(\sigma,\baddr,\eaddr)},\\\sealed{\sigma,\vsc_D}\endarray\right)} \;\middle| \;
    \begin{array}{l}
      \vsc_D = ((\rw,\linear),\baddr,\eaddr,\baddr-1) \wedge\\
      \exists r \in \addressable{\linear,W} \ldotp \\
      \quad  \exists \stpair{\ms}{\ms} \ldotp \\
      \qquad \dom(\src{\ms_S}) = \dom(\ms_T) = [\baddr, \eaddr] \wedge \stareg{\spao} \nequal W(r) \wedge \\
      \qquad \forall W' \privft W \ldotp \\
      \qquad \quad \exists r', W'(r') = W(r), \exists r'', W'(r'') = \stdreg{[\stkb,\eaddr]}{\spao} \ldotp \\
      \qquad \qquad { \color{red} \forall (\src{c}, c') \in H_\sigma (\sigma) \ldotp \npair{\src{c,\retptrd(\sigma,\baddr,\eaddr)}, c' , \sealed{\sigma,\vsc_D}} \in \lrk(W') }%\text{\lau{This needs some work - specifically what i c and c' and do we need to seal them?}}

>>>>

% \dominique{7-9-2017: Should we keep local/global and linear/non-linear?  I was thinking just the latter would suffice...}
% \lau{07-09-2017: The local/global mechanism still has some value as it now can be used for the purpose of arguments that cannot be stored by the receiver (if you are willing to ``pay'' the clearing cost). I do, however, not think that it is strictly necessary here to make things work.}
% \lau{12-09-2017: I will remove the local capabilities today for the reasons we have discussed (they add to the complexity and they seem to be of little to no use without a clear memory instruction).}
Source language domains:
\[
  \begin{array}{rrcl}
   \addrbnf,\basebnf \in & \Addr & \defeq & \nats \\
    \sealbasebnf, \sigma \in & \Seal & \defeq & \nats \\
    &\Word & \defeq & \ints \uplus \SealableCaps\\
    \permbnf \in& \Perm & \defbnf & \dots \\
    &\linbnf & \defbnf & \linear \mid \normal \\
    &\aendbnf & \in & \Addr \uplus \{\infty \} \\
    &\sealendbnf & \in & \Seal \uplus \{\infty \} \\
    &\scbnf &\defbnf & ((\permbnf,\linbnf),\basebnf,\aendbnf,\addrbnf) \mid \seal{\linbnf,\sealbasebnf,\sealendbnf,\sigma}\\
    & & & {\sourcecolor{} \mid \stkptr{\permbnf,\basebnf,\aendbnf,\addrbnf}}\\ 
    &\cbnf & \defbnf &  \scbnf \mid \sealed{\sigma,\scbnf}{\sourcecolor{} \; \mid \retptrd(\sigma,(\basebnf,\aendbnf)) \mid \retptrc(\sigma,(\permbnf,\linbnf,\basebnf,\aendbnf,\addrbnf))}\\ 
    &\rbnf & \defbnf &\pcreg \mid \rret \mid \rstk \mid \rdata \mid \dots \\
    &\Reg & \defeq & \RegName \fun \Word\\
    &\Mem & \defeq & \Addr \fun \Word \\
    &\MemSeg & \defeq & \Addr \parfun \Word \\
    {\sourcecolor \sstkframe \in} & {\sourcecolor \StkFrame} & {\sourcecolor \defeq} & {\sourcecolor \Caps \times \MemSeg \times \Addr}\\
    \src{\sstk \in}& \src{ \Stack} & \src{ \defeq} & \src{ \StkFrame^*} \\
    \Phi \in & \ExecConf & \defeq & \Mem \times \Reg {\sourcecolor{} \; \times \; \Stack \times \MemSeg }\\
    &\Conf & \defeq & \ExecConf \uplus \{\failed\} \uplus (\{\halted\} \times \Mem)
  \end{array}
\]
\lau{06-09-2017: Should seals also have the option to be linear?}
\lau{13-09-2017: For now I have added linearity to the seals.}
\dominique{27-9-2017: I think we should have versions of $\retptrd$ and $\retptrc$ for non-top stack frames and define that invoking them with the current stack pointer will fail.}
\lau{28-09-2017: Why would you like this? If we want to add this, we will have to be careful, because an old code-return-pointer may fit perfectly well with our new data-return-pointer, so in this case it should not fail. We added the seal to the return pointers, so we had some way of figuring out whether two return pointers would actually fit together.}
\dominique{27-9-2017: Likewise, I think we need to have a source-language representation for a pointer into one of the non-top stack frames, as we may need to be able to back-translate adversary code that reads/writes in those.}
\lau{28-09-2017: At the moment, the only part of the stack that is stored in the stack frame is the private part. Specifically it is the part from the base to the current address of the stack pointer \emph{in $r_\stk$}. This means that if someone saves a stack pointer, so it is not included in the call, then they can still use it because that part of the stack was not encapsulated in a stack frame. Makes sense?}
The target language domains are all the non blue parts in the above. The source language domains are the black and blue parts in the above. Further
\begin{itemize}
\item $\linbnf$ defines domain $\Linear$
\item $\scbnf$ defines domain $\SealableCaps$
\item $\cbnf$ defines domain $\Caps$
\item $\rbnf$ defines the finite set $\RegName$.
\item $\Perm$ is defined as the set of permissions in Figure~\ref{fig:perm-hier}.
\end{itemize}

@@

\[
  \isLinear{\cb} \defeq
  \begin{cases}
    \top & 
    \arraycolsep=0pt
    \begin{array}[t]{l}
      \cb = ((\_,\linear),\_,\_,\_) \tor\\
      \cb = \seal{\linear,\_,\_,\_} \tor\\
      \cb = \sealed{\_,\cb'} \tand \isLinear{\cb'} 
    \end{array}\\
    \src{\top} & 
    \sourcecolor\left.
    \arraycolsep=0pt
    \begin{array}[t]{l}
      \cb = \stkptr{\_,\_,\_,\_}\\
      \cb = \retptrd(\_,\_)
    \end{array}\right.\\
    \bot & \totherwise
  \end{cases}
\]

@@

\noindent\textbf{xjmp}\\
\lau{22-09-2017: Can we allow the callee to return any stack pointer? At the moment, it is not possible to create an empty stack pointer which may be a saving grace. If we at some point change this, so you can split capabilities into empty ones, then we need to consider whether it is safe for callees to return empty stacks (I think it is okay as long as we always have some stack usage).}
\lau{28-09-2017: For now, the jump to a return pointer does the stack end point check. We could possibly move this to the proposed semantic condition as well.}
\begin{align*}
  \sem{\txjmp{r_1}{r_2}}(\Phi) = &
                                   \begin{cases}
                                     \arraycolsep=0pt
                                     \begin{array}[t]{rl}
                                       \Phi & \updReg{r_1}{w_1}\\
                                            & \updReg{r_2}{w_2}\\
                                            & \updReg{\pcreg}{c_\code}\\
                                            & \updReg{\rdata}{c_\data}
                                     \end{array} &
                                     \begin{array}[t]{l}
                                       \Phi(r_1) = \sealed{\sigma,c_\code} \tand \\
                                       \Phi(r_2) = \sealed{\sigma,c_\data} \tand \\
                                       \nonExec{c_\data} \tand \\
                                       w_1 = \linCons{\Phi(r_1)} \tand \\
                                       w_2 = \linCons{\Phi(r_2)}
                                     \end{array}
                                     \\&\\
                                     \sourcecolor\left.
                                       \arraycolsep=0pt
                                       \begin{array}[t]{rl}
                                         \Phi' & \updReg{r_2}{0} \\
                                               & \updReg{\pcreg}{\opc}\\
                                               & \updReg{\rdata}{0}\\
                                               & \updReg{\rstk}{c_\stk}
                                       \end{array}\right.&
                                     \sourcecolor\left.
                                       \begin{array}[t]{l}
                                         \Phi(r_1) = \retptrc(\sigma,\_) \tand \\
                                         \Phi(r_2) = \retptrd(\sigma,(\aaddr_\stk,\_)) \tand \\
                                         \Phi(\rstk) = \stkptr{\rw,\stkb,\eaddr_\stk,\_} \tand \\
                                         \Phi = (\mem,\reg,\stkf::\stk,\ms_\stk) \tand \\
                                         \stkf = (\opc,\ms_{\stk,\priv}) \tand \\
                                         \dom(\ms_{\stk,\priv}) = [\eaddr_\stk+1,\eaddr_{\stk,\priv}] \tand\\
                                         c_\stk = \stkptr{\rw,\stkb,\eaddr_{\stk,\priv},\aaddr_\stk} \tand\\
                                         \Phi' = (\mem,\reg,\stk,\ms_{\stk,\priv} \uplus \ms_\stk) 
                                       \end{array}\right.
                                     \\
                                     \failed & \totherwise
                                   \end{cases}
\end{align*}

\noindent\textbf{cseal}\\
\begin{align*}
  \sem{\tcseal{r_1}{r_2}{r_3}}(\Phi) = &
                                  \begin{cases}
                                    \updPcAddr{}\left(
                                    \arraycolsep=0pt
                                    \begin{array}{rl}
                                      \Phi&\updReg{r_1}{\vsc}\\
                                          &\updReg{r_2}{w_2}
                                    \end{array}\right)
&
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \Phi(r_2) \in \SealableCaps \tand \\
                                      \Phi(r_3) = \seal{\lin, \sigma_\baddr, \sigma_\eaddr,\sigma} \tand \\
                                      \sigma_\baddr \leq \sigma \leq \sigma_\eaddr \tand \\ 
                                      \vsc = \sealed{\sigma,\Phi(r_2)} \tand\\
                                      w_2 = \linCons{\Phi(r_2)}                                     
                                    \end{array}
                                    \\
                                    \failed & \totherwise
                                  \end{cases}
\end{align*}

@@

                                                   \Phi(r_1) = \sealed{\sigma_1,c_1} \tand \\
                                                   \Phi(r_2) = \sealed{\sigma_2,c_2} \tand \\

@@

\subsubsection{Programs}
Here we define what constitutes a program.
\lau{05-10-2017: It seems like both program and context takes care of linking atm.}
\begin{definition}
  \label{def:program}
  \lau{27-09-2017: The ``somehow''s need to be fixed.}
  A program, $\program$ consists of two sealed capabilities, $\vsc_\code = \sealed{\sigma,c_\code}$ and $\vsc_\data = \sealed{\sigma,c_\data}$, and and two memory segments $\ms$ and $\ms_\link$ satisfying
  \begin{itemize}
  \item $c_\code = ((\rx,\lin_\code),\baddr_\code,\eaddr_\code,\aaddr_\code)$ where $\aaddr = \baddr + 2$ and $[\baddr_\code,\eaddr_\code]\subseteq \dom(\ms)$
  \item $c_\data = ((\rw,\lin_\data),\baddr_\data,\eaddr_\data,\baddr_\data)$ where $[\baddr_\data,\eaddr_\data] \subseteq \dom(\ms)$ and $[\baddr_\code,\eaddr_\code] \cap [\baddr_\data,\eaddr_\data] = \emptyset$
  \item $\ms$ and $[c_\code,c_\data]$ are self-contained with $\ms_\link$ as slack.
  \item $\ms$ respects write-xor-execute.
  \item $\ms(\baddr_\code) = \seal{\normal,\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}$ where these are somehow the sufficient amount of seals.
  \item $\ms(\baddr_\code+1) = ((\ro,\normal),\baddr_\link, \eaddr_\link, \baddr_\link)$ where $\dom(\ms_\link) = [\baddr_\link, \eaddr_\link]$
  \end{itemize}
\end{definition}
\lau{27-09-2017: At the moment, we do not have the proper support to let the code capability be linear (in the sense that you cannot write a sensible program) - maybe we should just require the code capability to be normal.}

@@

\[
  \begin{array}{rl}
  \lrk(W) = &\left\{ \npair{\left(\array{l}\src{\retptrc(\sigma,(\perm,\lin,\baddr_c,\eaddr_c,\aaddr_c))},\\\src{\retptrd(\sigma,(\aaddr_d,\eaddr_d))},\\k_{c,T},k_{d,T}\endarray\right)} \middle|
    \begin{array}{l}
      k_{d,T} = \sealed{\sigma,c_d} \wedge\\
      k_{c,T} = \sealed{\sigma,c_c} \wedge\\
      c_c = ((\perm,\lin),\baddr_c,\eaddr_c,\aaddr_c) \wedge\\
      c_d = ((\rw,\linear),\aaddr_d,\eaddr_d,\aaddr_d-1) \wedge\\
      \npair[n]{[\stpair[.]{\retptrc(\sigma,\_)}{k_{c,T}},\stpair[.]{\retptrd(\sigma,\_)}{k_{d,T}}]} \in \lrp(W) \wedge \\
      \forall n' \leq n, W' \pubft W \ldotp \\
      \quad \forall W_\lrr, W_\lrm \ldotp  \\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk::(\opc,\ms_{\stk,f}),\ms_\stk}{\ms_T}}{W_\lrm} \wedge \\
      \qquad\opc = c_c \wedge\\
      \qquad\dom(\ms_{\stk,f}) = [\aaddr_d,\eaddr_d] \wedge\\
      \qquad\npair[n']{\array{l}\src{\reg_S\update{\rstk}{\stkptr{\rw,\stkb,\eaddr_d,\aaddr_d}}},\\
                               {\reg_T\update{\rstk}{((\rw,\linear),\stkb,\eaddr_d,\aaddr_d)}}\endarray}\in \lrr(\{r_\stk\})(W_\lrr) \wedge\\ 
      \qquad\npair[n']{[(\opc,\opc)]} \in \lrp(W')\\
      \qquad\Rightarrow\\
      \qquad \npair[n']{\left(\arraycolsep=0pt\array{l}
                          \left(\arraycolsep=0pt\array{l}
                            \src{\ms_S,\reg_S\update{\pcreg,\rstk}{\opc,\stkptr{\rw,\stkb,\eaddr_d,\aaddr_d}},}\\
                            \src{\stk, \ms_\stk \uplus \ms_{\stk,f}}
                          \endarray \right) \\
                          \left(\ms_T,\reg_T\update{\pcreg,\rstk}{\opc,((\rw,\linear),\stkb,\eaddr_d,\aaddr_d)} \right)
                        \endarray \right)} \in \lro(W'\oplus W_\lrr \oplus W_\lrm)
    \end{array}
  \right\}\\ \cup
    & \left\{ \npair{\left( k_{c,S},k_{d,S},k_{c,T},k_{d,T} \right)} \middle|
      \begin{array}{l}
        \pi_\sigma(k_{c,S}) = \pi_\sigma(k_{d,S}) \wedge \pi_\sigma(k_{c,T}) = \pi_\sigma(k_{d,T}) \wedge \npair{(k_{c,S},k_{c,T}),(k_{d,S},k_{d,T})} \in \lrp(W) \\
        \forall n' \leq n, W' \pubft W \ldotp \\
        \quad \npair[n']{(k_{c,S},k_{c,T}),(k_{d,S},k_{d,T})} \in \lrp(W) \Rightarrow\\
        \qquad \forall \npair[n']{\stpair{\reg}{\reg}} \in \lrr(\{\rdata\})(W'_\lrr) \ldotp 
               \forall \memSat[n']{\src{\ms_S,\stk,\ms_\stk},\ms_T}{W'_\lrm} \ldotp\\
        \qquad \quad \npair[n']{\left(
        \arraycolsep=0pt\array{l}
          (\src{\ms_S},\src{\reg_S}\update{\pcreg,\rdata}{\pi_\vsc(\src{k_{c,S}}),\pi_\vsc(\src{k_{d,S}})},\src{\stk},\src{\ms_\stk})\\
          (\ms_T,\reg_T\update{\pcreg,\rdata}{\pi_\vsc(k_{c,T}),\pi_\vsc(k_{d,T})})
        \endarray\right)} \in \lro(W' \oplus W'_\lrr \oplus W'_\lrm)
      \end{array}
      \right\}
  \end{array}
\]

@@

\[
  \lrr(R)(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : \RegName \fun \World \ldotp \\
      \quad W = \bigoplus_{r \in \RegName} S(r) \\
      \quad \forall r \in \RegName \setminus (\{\pcreg \} \cup R)\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrv(S(r))
    \end{array}
            \right\}
\]
Where $S\text{ is a separation of $W$}$ means that no two partition share the same ``spatial'' region (whatever that is).

\lau{TODO: Rewrite the other definitions to pass around $H_\sigma$ (if this is how we want to handle seals.)}
\[
  \lrv(H_\sigma,W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrc(\sigma,\perm,\lin,\baddr,\eaddr,\aaddr)},\\\sealed{\sigma,\vsc_C}\endarray\right)} \;\middle| \;
    \begin{array}{l}
      \vsc_c = ((\perm,\lin),\baddr,\eaddr,\aaddr) \wedge \\
      \forall (\src{c},c') \in H_\sigma(\sigma) \ldotp \\
      \quad \exists r \in \addressable{\linear,W} \ldotp \\
      \qquad  \exists \stpair{\ms}{\ms} \ldotp \\
      \qquad \quad \dom(\src{\ms_S}) = \dom(\ms_T) = [\pi_\baddr(c), \pi_\eaddr (c)] \wedge \stareg{\spao} \nequal W(r) \wedge \\
      \qquad \qquad \forall W' \privft W \ldotp \\
      \qquad \qquad \quad \exists r', W'(r') = W(r), \exists r'', W'(r'') = \stdreg{[\stkb,\eaddr]}{\spao} \ldotp \\
      \qquad \qquad \qquad { \color{red} \npair{(\src{\retptrc(\sigma,\perm,\lin,\baddr,\eaddr,\aaddr)}, \src{c}, \sealed{\sigma,\vsc_c}, c')}} \in \lrk(W')
    \end{array}
    \right\}\cup\\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrd(\sigma,\baddr,\eaddr)},\\\sealed{\sigma,\vsc_D}\endarray\right)} \;\middle| \;
    \begin{array}{l}
      \vsc_D = ((\rw,\linear),\baddr,\eaddr,\baddr-1) \wedge\\
      \exists r \in \addressable{\linear,W} \ldotp \\
      \quad  \exists \stpair{\ms}{\ms} \ldotp \\
      \qquad \dom(\src{\ms_S}) = \dom(\ms_T) = [\baddr, \eaddr] \wedge \stareg{\spao} \nequal W(r) \wedge \\
      \qquad \forall W' \privft W \ldotp \\
      \qquad \quad \exists r', W'(r') = W(r), \exists r'', W'(r'') = \stdreg{[\stkb,\eaddr]}{\spao} \ldotp \\
      \qquad \qquad { \color{red} \forall (\src{c}, c') \in H_\sigma (\sigma) \ldotp \npair{\src{c,\retptrd(\sigma,\baddr,\eaddr)}, c' , \sealed{\sigma,\vsc_D}} \in \lrk(W') }%\text{\lau{This needs some work - specifically what i c and c' and do we need to seal them?}}
